---
title: "intrestingVarsGraphs"
author: "Max Scott"
date: "10/3/2021"
output: pdf_document
---

TODO 
writen report 
  make sure all graphs are related to zip code 
  do per revew stuff 
pawer poit 
  put stuff in pawer poit 
  use writen report as guid 
  have some structre 


my vars 

poverty [X]
sexual oriantation [] ( not enuf data)
income [X]
zip code [X] 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
d


```{r}
intrestingGroups <- MentalHealth %>% 
  select(gender,poverty,annual_household_income,race_id,age,health_insurance,employment_status,education_level,sexual_orientation,relationship_status,zipcode, pandemic_after)
head(intrestingGroups)
```

```{r}
intrestingGroups %>% 
  ggplot() + geom_bar( aes(x = health_insurance, fill=pandemic_after))
```


```{r}
poverty <- intrestingGroups %>% 
  filter(poverty == 1)
poverty

poverty %>% 
  ggplot(aes( pandemic_after)) + geom_histogram(fill = "blue") + theme_bw() + xlab("After Pandemic")
```
annual_household_income 
pandemic_after

```{r}
not_poverty <- intrestingGroups %>% 
  filter(poverty == 0)
not_poverty

not_poverty %>% 
  ggplot() + geom_histogram( aes(x = pandemic_after ),fill = "blue")+ theme_bw() + xlab("After Pandemic")
```


```{r}


intrestingGroups %>% 
  ggplot() + geom_histogram( aes(x = pandemic_after), fill = "blue") + facet_wrap(vars(education_level)) + theme_dark()
```

sexual oriantation 
Asexual  (1)  
Bisexual  (2)  
Homosexual  (3)  
Heterosexual or straight  (4)  
Pansexual  (5)  
Other  (6)

gender (dont know what is waht)
Male   
Female  
Non-binary   
Other 

88.19 % of all data is in group Heterosexual 
```{r}
MentalHealth %>% 
  ggplot() + geom_bar( aes(x = sexual_orientation, fill = as.factor(gender))) + coord_flip() + theme_bw() + xlab("Sexual Orientation") + scale_x_discrete( labels = c("2" = "b", "4" ="d"  ,"6" ="f"))

#plain vinila 
MentalHealth %>% 
  ggplot() + geom_bar( aes(x = sexual_orientation, fill = as.factor(gender))) + theme_bw()

#ingnor this for now / just trying to understand what 4 and 6 are for gender 
MentalHealth %>% 
  ggplot() + geom_bar( aes(x = sexual_orientation, fill = as.factor(gender))) + facet_wrap(vars(sexual_orientation))


fours <- intrestingGroups %>% 
  select(sexual_orientation) %>% 
  filter(sexual_orientation==4) %>% 
  nrow()
totol <- intrestingGroups %>% 
  select(sexual_orientation) %>% 
  nrow()


# mathy stuff 
totol
fours

(fours/totol)*100
(totol - fours) / 5

```


p-valu of 0.0143 implies that there is significant difrenc in mental health among difrent sexual oriantations 

# dont say that you can draw a conclushion 

```{r}
champagne_supernova <- aov(pandemic_after ~ sexual_orientation, data = intrestingGroups)

#summary(one.way)
```




**************** start on zipcode ****************





```{r}
intrestingGroups %>% 
  filter(zipcode != 16652 ) %>% 
  ggplot() + geom_histogram(aes(x = pandemic_after)) + facet_wrap(vars(zipcode))

notHuntington <- intrestingGroups %>% 
  filter(zipcode != 16652 ) %>% 
  nrow()

notHuntington

notHuntington / 28
```

```{r}
intrestingGroups %>% 
  filter(zipcode != 16652) %>% 
  ggplot() + geom_histogram(aes(x = pandemic_after))
  
```

```{r}
intrestingGroups %>% 
  filter(zipcode == 16652) %>% 
  ggplot() + geom_histogram(aes(x = pandemic_after))
```


********************   zipcode and income *******************

income among huntingdon  people 
```{r}

intrestingGroups %>%
  filter(zipcode == 16611) %>% 
  ggplot() + geom_bar(aes(x = annual_household_income)) 
```

incom among all non huntingdon people 

```{r}
intrestingGroups %>%
  filter(zipcode != 16611) %>% 
  ggplot() + geom_bar(aes(x = annual_household_income)) 
```

```{r}
intrestingGroups %>% 
  select(annual_household_income)
```



********************   sexual oriantation and zipcode  *******************
```{r}

```
************** sexual oriantation and poverty as related to mental health 
```{r}
not_poverty <- intrestingGroups %>% 
  filter(poverty == 1)
not_poverty

not_poverty %>% 
  ggplot() + geom_histogram(aes(x = pandemic_after)) + facet_wrap(vars(sexual_orientation))

```

```{r}
poverty <- intrestingGroups %>% 
  filter(poverty == 0)
poverty

```

```{r}
intrestingGroups %>%
  
  ggplot() + geom_bar(aes(x = annual_household_income)) 

intrestingGroups %>%
  select(annual_household_income)

intrestingGroups %>% 
  ggplot() + geom_histogram(aes(x = pandemic_after), fill = "blue") + facet_wrap(vars(annual_household_income)) + theme_bw() + xlab("After Pandemic")
```

over 50,000 seams to increas your odds of hving exilent mental health status  

```{r}
MentalHealth %>% 
  select(travel_time)

MentalHealth %>% 
  filter( travel_time != 6) %>% 
  ggplot() + geom_bar(aes(x = travel_time))
```

most peole would only haveto travel 5-15 minuts to get to a profeshinal for help while very few wouldhave to travle more than an huer. 


```{r}
MentalHealth %>%
  filter(zipcode != 16652) %>% 
  ggplot() + geom_bar(aes(x = poverty)) + facet_wrap(vars(zipcode))
```





```{r}
MentalHealth %>% 
  group_by(zip_region) %>% 
  summarize( MFV = mfv(annual_household_income)) 
  
```

```{r}
MentalHealth %>%
  filter(zipcode != 16652) %>% 
  ggplot() + geom_bar(aes(x = as.factor(annual_household_income)), fill = "blue") + facet_wrap(vars(zipcode)) + theme_bw() + labs(x = "Annual Household Income") + coord_flip() + scale_x_discrete(labels= c("5-10 min", "", "asdf", "", "slfkj", "", "sfd", ""))  

```



```{r}
MentalHealth %>%
  filter(zipcode != 16652) %>% 
  ggplot() + geom_bar(aes(x = as.factor(annual_household_income)), fill = "blue") + facet_wrap(vars(zipcode)) + theme_bw() + labs(x = "Annual Household Income") + coord_flip() + scale_x_discrete(labels= c("5-10 min", "", "asdf", "", "slfkj", "", "sfd", ""))  

MentalHealth %>% 
  filter(zipcode == 16652) %>% 
  ggplot() + geom_bar(aes(x = annual_household_income), fill ="blue") + theme_bw() + labs(x = "Annual Household Income") 

MentalHealth %>%
  #filter(zipcode != 16652) %>% 
  ggplot() + geom_bar(aes(x = as.factor(annual_household_income)), fill = "2020ff") + facet_wrap(vars(zip_region)) + theme_bw() + labs(x = "Annual Household Income") + coord_flip() + scale_x_discrete(labels= c("5-10 min", "", "asdf", "", "slfkj", "", "sfd", ""))  

Mental_mod <- MentalHealth %>%
  # Rename 4 to 4wd, f to Front, r to Rear
  filter(zip_region != 999) %>% 
  mutate(zip_region = recode(zip_region, "1" = "Juniata Valley", "2" = "Huntingdon", "3" = "Mount Union", "4" = "Suthern Huntingdon", "5" = "Mifflin Juniata", "999" = "Other"))

Mental_mod %>%
  #filter(zip_region != 999) %>% 
  ggplot() + geom_bar(aes(x = as.factor(annual_household_income)), fill = "light blue") + facet_wrap(vars(zip_region)) + theme_bw() + labs(x = "Annual Household Income", y = "Number of Respondents") + coord_flip() + scale_x_discrete(labels= c("No Income", "Under $15,000", "$15,000 - $29,999", "$30,000 - $49,999", "$50,000 - $74,999", "$75,000 - $99,999", "$100,000 -$150,000", "Over $150,000"))  
```




```{r}
cases <- MentalHealth %>% 
  filter(travel_time == 5) %>% 
  #filter(zipcode == 43026) %>% 
  select(travel_time, zipcode) 

cases

cases2 <- MentalHealth %>% 
  filter(travel_time == 1) %>% 
  #filter(zipcode == 43026) %>% 
  select(travel_time, zipcode) 

cases2
9/10
```




```{r}

MentalHealth %>% 
  filter(travel_time != 6) %>% 
  #filter(zipcode != 16652) %>% 
  ggplot() + geom_bar(aes(x = as.factor(travel_time), fill = as.factor(zipcode)), position = "fill" ) + theme_bw(base_size = 22) + 
scale_x_discrete(labels= c("5-10 min", "16 - 30 min", " 31 - 45 min", " 46 - 60 min", "more than 1 hour"))  + labs(fill = "Zip Code") + labs( x = "Travel Time" , y = "Number of Respondents" ) 

```
question 52 ( trabel_time)
1 = 5-10
2 = 16 - 30 
3 = 31 - 45
4 = 46 - 60 
5 = >1 h 
6 = other 


question 42_5 ( ranked_finding_transportaiontoni)

1 = extremely eazy 
2 = moderitly eazy 
3 = ... 

7 = extreamly dificult 





```{r}

MentalHealth %>% 
  filter(travel_time != 6) %>% 
  #filter(zipcode != 16652) %>% 
  ggplot() + geom_bar(aes(x = ranking_finding_transportation, fill = as.factor(zipcode)), position = "fill" ) 

```
from this graph and the last collor graph it apers that thir is not a strang relation between travle time and dificulty with transportation. 


question 52 ( trabel_time)
1 = 5-10
2 = 16 - 30 
3 = 31 - 45
4 = 46 - 60 
5 = >1 h 
6 = other 


question 42_5 ( ranked_finding_transportaiontoni)

1 = extremely eazy 
2 = moderitly eazy 
3 = ... 

7 = extreamly dificult 

```{r}

MentalHealth %>% 
  ggplot() + geom_bar(aes(x = ranking_finding_transportation))

table(MentalHealth$ranking_finding_transportation, MentalHealth$travel_time )
```



```{r}

newHelth <- MentalHealth %>% 
  mutate(ranking_finding_transportation = ranking_finding_transportation + 1)
newHelth <- newHelth %>% 
  mutate(travel_time = travel_time + 1)


table(MentalHealth$ranking_finding_transportation, MentalHealth$travel_time )
table(newHelth$ranking_finding_transportation, newHelth$travel_time )


MentalHealth %>% 
  count(ranking_finding_transportation , travel_time) %>%  
  ggplot(mapping = aes(x = ranking_finding_transportation , y = travel_time)) +
    geom_tile(mapping = aes(fill = n))
```



```{r}
MentalHealth %>% 
  ggplot() + geom_count( aes(x = as.factor(travel_time), y = ranking_finding_transportation, color = as.factor(zipcode))) + theme_bw(base_size = 22) +scale_x_discrete(labels= c("5-10 min", "16 - 30 min", " 31 - 45 min", " 46 - 60 min", "more than 1 hour", "other"))  + labs(x = "Travel Time", y = "Finding Transportation", color = "Zip Code", size = "Number of Cases")


MentalHealth %>% 
  ggplot() + geom_count( aes(x = travel_time, y = ranking_finding_transportation, color = as.factor(zipcode)))  + facet_wrap(vars(zipcode)) 
```



```{r}
means <- MentalHealth %>% 
  summarize(mean_finding_good_service_provider = mean(ranking_finding_a_provider, na.rm = TRUE))


means <- means %>% 
  pivot_longer(-0, names_to = "what_chalenge" ,values_to = "the_means") 

means <- means %>% 
  arrange(desc(the_means))
means
```











