---
title: "question 35 secont try"
author: "Max Scott"
date: "11/16/2021"
output: pdf_document
---
Do to a lack of data, observed and expected counts are two low and so fishers test is used insted where apropriate. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)

```


```{r}
MentalHealth <- read_csv("~/Desktop/csvData/client_data_sept29_partial_rename.csv")
head(MentalHealth)
```

rating_treatment_type_selectiont X
rating_find_first_appointment	X
rating_find_a_provider	X
ranking_finding_childcare X
rating_finding_time	X
are the top 5 greatest dificultys and will be anilized here 

```{r}
withOut5999 <- MentalHealth %>% 
  filter(zip_region != 5 & zip_region != 999)
```






```{r}
table(withOut5999$zip_region,withOut5999$ranking_finding_a_provider)
```






H0: difficulty level and Zip Code/ Zip Region are  independent 
Ha: difficulty level  and Zip Code/ Zip Region are dependent 

```{r}
struglData <- crime_data <- matrix(c(1,18,0,3,
                                     2,18,2,3,
                                     0,9 ,1,4,
                                     1,4 ,1,1,
                                     2,5 ,3,0,
                                     1,12,2,0,
                                     0,3 ,2,2), 
nrow = 4)

struglData





```

expected counts 
```{r}
test_results <- chisq.test(struglData)
test_results$expected

```

espected is les tham 5 
do fishers exect 

```{r}
test_results <- fisher.test(struglData, simulate.p.value =  TRUE)
test_results
```




```{r}
table(withOut5999$zip_region,withOut5999$rating_find_first_appointment)
```


```{r}
struglData1 <- matrix(c(1,6 ,1,1,
                                     2,17,2,0,
                                     0,3 ,1,1,
                                     0,4 ,0,0,
                                     0,5 ,1,0,
                                     2,9 ,2,0,
                                     0,2 ,0,1), 
nrow = 4)

struglData1


```
expected counts 
```{r}
test_results1 <- chisq.test(struglData1)
test_results1$expected

```
less thn 5 so fishers 

```{r}
test_results <- fisher.test(struglData1, simulate.p.value =  TRUE)

test_results
```




```{r}
table(withOut5999$zip_region,withOut5999$ranking_finding_childcare)
```

```{r}
struglData2 <- matrix(c(3,11,2,8,
                                      1,7 ,0,0,
                                      0,6 ,0,2,
                                      1,32,6,2,
                                      1,6 ,2,0,
                                      0,4 ,0,0,
                                      1,3 ,1,1), 
nrow = 4)

struglData2


```

expected counts 
```{r}
test_results2 <- chisq.test(struglData2)
test_results2$expected

```

less then 5 so use fishers 
```{r}
test_results <- fisher.test(struglData2, simulate.p.value =  TRUE)

test_results
```


```{r}
table(withOut5999$zip_region,withOut5999$rating_finding_time)
```


```{r}
struglData3 <- matrix(c(
                                      1,13,1,1,
                                      1,12,1,1,
                                      1,5 ,1,0,
                                      0,5 ,1,0,
                                      1,10,2,0,
                                      1,2 ,0,0,
                                      0, 0 ,1,1), 
nrow = 4)

struglData3


```

expected counts 
```{r}
test_results3 <- chisq.test(struglData3)
test_results3$expected

```
less the n5 so fishers 

```{r}
test_results <- fisher.test(struglData3, simulate.p.value =  TRUE)

test_results
```



rating_treatment_type_selectiont



```{r}
table(withOut5999$zip_region,withOut5999$rating_treatment_type_selection)
```





```{r}
struglData4 <- matrix(c(
                                      1,6 ,0,1,
                                      0,10,2,0,
                                      0,7 ,2,0,
                                      0,9 ,0,0,
                                      2,8 ,0,1,
                                      2,6 ,2,1,
                                      0,1 ,1,0 ), 
nrow = 4)

struglData4


```

```{r}
test_results4 <- chisq.test(struglData4)
test_results4$expected
```

less them 5 so fishers 
```{r}
test_results <- fisher.test(struglData4, simulate.p.value =  TRUE)

test_results
```


random junk 
```{r}
prop.test(x = c(490, 400), n = c(500, 500),
              alternative = "two.sided")

```


